
\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}

\definecolor{AccentBlue}{HTML}{1F4E79}
\hypersetup{
  colorlinks=true,
  urlcolor=AccentBlue,
  linkcolor=AccentBlue
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.15em, itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt}
\renewcommand{\labelitemi}{\textbullet}

\newcommand{\cvsection}[1]{%
  \vspace{6pt}%
  {\large\bfseries\color{AccentBlue} #1}\\[-2pt]%
  {\color{AccentBlue}\hrule height 0.45pt}%
  \vspace{3pt}%
}
\newcommand{\cvrow}[2]{%
  \begin{tabularx}{\linewidth}{@{}X>{\raggedleft\arraybackslash}p{0.30\linewidth}@{}}
    #1 & #2
  \end{tabularx}
}
\newcommand{\cventryspace}{\vspace{2pt}}

\begin{document}

\begin{center}
  {\LARGE\bfseries Alex Example}\\[3pt]
  \small\href{mailto:alex.example@email.com}{alex.example@email.com} $\vert$ +44 7700 900123 $\vert$ London, UK $\vert$ \href{\detokenize{https://github.com/alex-example}}{GitHub} $\vert$ \href{\detokenize{https://www.linkedin.com/in/alex-example}}{LinkedIn} $\vert$ \href{\detokenize{https://alexexample.dev}}{Portfolio} $\vert$ \href{\detokenize{https://blog.alexexample.dev}}{Blog} $\vert$ \href{\detokenize{https://www.kaggle.com/alexexample}}{Kaggle} $\vert$ \href{\detokenize{https://devpost.com/alexexample}}{Devpost} $\vert$ \href{\detokenize{https://scholar.google.com/citations?user=example}}{Google Scholar}
\end{center}

\cvsection{ Profile }
Computer engineering student focused on machine learning systems, backend software, and practical technology communities.

\cvsection{ Education }
\cvrow{\textbf{ Northbridge University }}{ 2023 -- 2027 }
\cvrow{ BSc Computer Engineering, First Class Honours expected}{ London, UK }
\textit{Relevant Coursework:} Data Structures \& Algorithms, Machine Learning, Distributed Systems, Database Systems, Probability \& Statistics
\begin{itemize}
  \item Named to the Dean's List for strong academic performance across software engineering and mathematics modules.
  \item Led a four-person coursework project that evaluated supervised learning models for tabular prediction.
\end{itemize}
\cventryspace

\cvsection{ Experience }
\cvrow{\textbf{ Startup Events Coordinator }}{ Jan 2025 -- Present }
\cvrow{ FounderHub Society \textbar{} \textit{ Notion, Airtable, Mailchimp, Canva }}{ London, UK }
\begin{itemize}
  \item Organised a 180-attendee founder panel by coordinating speakers, venue operations, promotion, and volunteer staffing.
  \item Secured sponsorship support through targeted outreach emails, follow-up calls, and partner relationship management.
  \item Created event recaps and founder interview posts that increased community newsletter engagement.
\end{itemize}
\cventryspace
\cvrow{\textbf{ Software Engineering Intern }}{ Jun 2025 -- Sep 2025 }
\cvrow{ ExampleCorp \textbar{} \textit{ Python, FastAPI, PostgreSQL, Docker, GitHub Actions }}{ London, UK }
\begin{itemize}
  \item Presented sprint demos to product managers and analysts, translating engineering trade-offs into clear delivery decisions.
  \item Added integration tests and CI checks that caught schema regressions before deployment.
\end{itemize}
\cventryspace

\cvsection{ Projects }
\cvrow{\textbf{ Campus Startup Weekend Platform } -- \href{\detokenize{https://devpost.com/software/campus-startup-weekend-platform}}{Devpost}}{ 2025 }
\cvrow{ Event operations and team matching tool }{ \textit{ TypeScript, Next.js, Airtable, Vercel } }
\begin{itemize}
  \item Designed participant intake and team matching workflows for designers, engineers, and business-focused attendees.
  \item Coordinated mentor booking slots and automated attendee updates during a live weekend event.
\end{itemize}
\cventryspace
\cvrow{\textbf{ ML Model Monitoring Dashboard } -- \href{\detokenize{https://github.com/alex-example/ml-monitoring-dashboard}}{GitHub} $\vert$ \href{\detokenize{https://alexexample.dev/ml-monitoring}}{Demo}}{ 2026 }
\cvrow{ Model evaluation and drift monitoring }{ \textit{ Python, Streamlit, scikit-learn, Pandas, Plotly } }
\begin{itemize}
  \item Visualised precision-recall curves, confusion matrices, and calibration plots for multiple model versions.
\end{itemize}
\cventryspace

\cvsection{ Leadership, Volunteering \& Outreach }
\begin{itemize}
  \item Division 5 Team Captain, University Badminton Club: coordinated training, scheduled fixtures with opposition captains, mentored junior teammates, and led match strategy.
  \item Core Member, Entrepreneurship Development Cell: secured monetary and non-monetary sponsors through outreach calls for a large student entrepreneurship event.
  \item Technical Blog Writer: published technical blogs on machine learning and project work.
\end{itemize}

\cvsection{ Skills }
\textbf{ Programming:} Python, TypeScript\\[1pt]\textbf{ Frontend:} React, Next.js, Streamlit\\[1pt]\textbf{ Tools:} Git, Notion, Airtable\\[1pt]\textbf{ Communication:} Technical writing, Public speaking, Stakeholder management, Sponsorship outreach, Event operations

\end{document}